Submission and Formatting Instructions for \\ International Conference on Machine Learning (ICML 2019)

### 2019-04-23 paper/icml_ai4good/main.tex
updated
will sort out table later

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

@@

\section{Case Study}
\subsection{Connecting a Stochastic Simulator to a Probabilistic Programming System}

@@

\section{Results}

TO ADD

>>>>

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables
\usepackage{tabularx}

@@

\section{Case Study}
\subsection{Connecting a Epidemiology Simulators to a Probabilistic Programming System}

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{graphicx}
% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{table*}[b!]
\footnotesize
\setlength{\tabcolsep}{1mm}
\caption{Addresses}
\label{table:addresses}
\def\arraystretch{1.25}
% \setlength{\tabcolsep}{1mm}
\begin{tabularx}{\textwidth}{@{}lX@{}} 
\toprule
Address & Physical event                                                                                                                            \midrule
1 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const)+0x28a; OM::Population::createInitialHumans()+0x94; OM::Population::newHuman(OM::SimTime)+0x5c; OM::Host::Human::Human(OM::SimTime)+0x12b; OM::WithinHost::WHInterface::createWithinHostModel(double)+0x99; OM::WithinHost::DescriptiveWithinHostModel::DescriptiveWithinHostModel(double)+0x3a; OM::WithinHost::WHFalciparum::WHFalciparum(double)+0xe6; OM::util::random::gauss(double, double)+0xb4]\_\_Normal\\
2 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0x1e9; OM::Population::newHuman(OM::SimTime)+0x5c; OM::Host::Human::Human(OM::SimTime)+0x12b; OM::WithinHost::WHInterface::createWithinHostModel(double)+0x99; OM::WithinHost::DescriptiveWithinHostModel::DescriptiveWithinHostModel(double)+0x3a; OM::WithinHost::WHFalciparum::WHFalciparum(double)+0xe6; OM::util::random::gauss(double, double)+0xb4]\_\_Normal\\
3 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x22c; OM::Host::InfectionIncidenceModel::numNewInfections(OM::Host::Human const\&, double)+0x2a3; OM::util::random::poisson(double)+0x13f]\_\_Poisson\\
4 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0x96; OM::Host::NeonatalMortality::eventNeonatalMortality()+0x9; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
5 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0x96; OM::Host::NeonatalMortality::eventNeonatalMortality()+0x9; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
6 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x280; OM::WithinHost::DescriptiveWithinHostModel::update(int, std::vector \textgreater{}\&, double, double)+0x3a2; OM::WithinHost::DescriptiveInfection::determineDensities(double, double, double, double\&, double, double)+0x303; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
7 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0x67; OM::WithinHost::WHFalciparum::determineMorbidity(OM::Host::Human\&, double, bool)+0x73; OM::WithinHost::Pathogenesis::PathogenesisModel::determineState(OM::Host::Human\&, double, double, double, bool)+0x143; OM::util::random::bernoulli(double)+0x47; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
8 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0x67; OM::WithinHost::WHFalciparum::determineMorbidity(OM::Host::Human\&, double, bool)+0x73; OM::WithinHost::Pathogenesis::PathogenesisModel::determineState(OM::Host::Human\&, double, double, double, bool)+0x162; OM::util::random::bernoulli(double)+0x47; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
9 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0x67; OM::WithinHost::WHFalciparum::determineMorbidity(OM::Host::Human\&, double, bool)+0x73; OM::WithinHost::Pathogenesis::PathogenesisModel::determineState(OM::Host::Human\&, double, double, double, bool)+0x1c7; OM::util::random::bernoulli(double)+0x47; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
10 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0xe3; OM::Clinical::ImmediateOutcomes::uncomplicatedEvent(OM::Host::Human\&, OM::Clinical::Episode::State)+0x87; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
11 & [forward()+0x204; OM::Simulator::start(scnXml::Monitoring const\&)+0x468; OM::Population::update1(OM::SimTime)+0xff; OM::Host::Human::update(bool)+0x2bc; OM::Clinical::ClinicalModel::update(OM::Host::Human\&, double, bool)+0xe8; OM::Clinical::CM5DayCommon::doClinicalUpdate(OM::Host::Human\&, double)+0xad; OM::Clinical::CM5DayCommon::severeMalaria(OM::Host::Human\&, OM::Clinical::Episode::State, double, int\&)+0x4b1; OM::util::random::uniform\_01()+0xc0]\_\_Uniform\\
\bottomrule                                                                                                                                   
\end{tabularx}
 \end{table*}
